Covariate analysis of MAYO reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-03-17 code/Rmd/MAYO_REPROCESSED.Rmd
Modified irwsva.build, num.sv and f.pvalue codes from sva package to include tolerance

knit2synapse::knitToFolderEntity(file = "./MAYO_REPROCESSED.Rmd",
                                 parentId = "syn7554308",
                                 entityName = 'MAYO Reprocessed RNASeq (Normalised)')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn8403743';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MAYO reprocessed RNASeq data';

@@

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=10, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>%
                   dplyr::filter(Comparison == 'Control-AD'), 
                 aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')

>>>>

knit2synapse::knitToFolderEntity(file = "./MAYO_REPROCESSED.Rmd",
                                 parentId = "syn8403743",
                                 entityName = 'MAYO Reprocessed RNASeq (Normalised)')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn8403743'
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MAYO reprocessed RNASeq data';

@@

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=5, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>%
                   dplyr::filter(Comparison == 'Control-AD'), 
                 aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')
